Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-07 PaperBCJ.tex
description_arquitectura

The availability of leading edge technologies  has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems.

\\

@@

Once the network architecture was chosen, it is constituted as follows: the input, a 64x64 RGB image layer followed by a convolution layer which reduces the image by taking only its main characteristics, then a layer of pooling which finds the maximum values of the characteristics found in the previous layer, followed by a second convolution, and a second layer of pooling, and finally two layers of type fully connected, from which in the end we have the output representing the two classes established in this network.\\

	\begin{figure}[h]
	\centering
	\includegraphics[width=3.6 in]{arquitectura}
	\caption{ The schematic of CNet }
	\label{fig_sim}
	\end{figure}

>>>>

The availability of leading edge technologies  has considerably increased, thus becoming more accessible to people. This effect of globalization has allowed many countries to have access to state-of-the-art technological products, promoting its application in different areas to generate alternative and more efficient solutions to conventional problems. \\

@@

The complete network model is formed as follows: the input layer where an RGB image 64x64 pixels, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel, this layer  obtaining only its main characteristics, then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2, then again a second layer of convolution is applied that has 16 filters, 5 kernels and a stride of 1, followed by a new layer of pooling with a kernel size and stride of 2 again obtained a size of 16x16x16 and finally the layers of type fully-connected with a total of 478 neurons, where the last two neurons that is the output represent the two classes established in this network.\\

	\begin{figure}[h]
	\centering
	\includegraphics[width=3.5 in]{arquitectura}
	\caption{ The schematic of CNet }
	\label{fig_sim}
	\end{figure}
